X-linked MethDep in early embryos, Zhu scWGBS data

### 2025-03-26 6.CT_methylation_in_early_embryos.Rmd
Add files via upload

>>>>

```
## t.tests

### Gametes stage

```{r}
t.test(bilan_selected %>% 
  filter(Genotype == "XX") %>% 
  filter(Stage == "MII Oocyte") %>% 
  pull(mean_met),
  bilan_selected %>% 
  filter(Genotype == "X") %>% 
  filter(Stage == "Sperm") %>% 
  pull(mean_met))
```

### at zygote stage

```{r}
stage <- "Zygote"
t.test(bilan_selected %>% 
  filter(Genotype == "XX") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met),
  bilan_selected %>% 
  filter(Genotype == "XY") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met))
```

### at 2-cell stage

```{r}
stage <- "2-cell"
t.test(bilan_selected %>% 
  filter(Genotype == "XX") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met),
  bilan_selected %>% 
  filter(Genotype == "XY") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met))
```

### at 4-cell stage

```{r}
stage <- "4-cell"
t.test(bilan_selected %>% 
  filter(Genotype == "XX") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met),
  bilan_selected %>% 
  filter(Genotype == "XY") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met))
```

### at 8-cell stage

```{r}
stage <- "8-cell"
t.test(bilan_selected %>% 
  filter(Genotype == "XX") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met),
  bilan_selected %>% 
  filter(Genotype == "XY") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met))
```
### at Morula stage

```{r}
stage <- "Morula"
t.test(bilan_selected %>% 
  filter(Genotype == "XX") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met),
  bilan_selected %>% 
  filter(Genotype == "XY") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met))
```

### at Blastocyst stage

```{r}
stage <- "Blastocyst"
t.test(bilan_selected %>% 
  filter(Genotype == "XX") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met),
  bilan_selected %>% 
  filter(Genotype == "XY") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met))
```

### at Post-implantation stage

```{r}
stage <- "Post-impl"
t.test(bilan_selected %>% 
  filter(Genotype == "XX") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met),
  bilan_selected %>% 
  filter(Genotype == "XY") %>% 
  filter(Stage == stage) %>% 
  pull(mean_met))
```
